Irt plot extra

### 2022-05-23 manuscript.Rmd
Introduction addedd

-   Light exposure is important

-   Light exposure Behaviour is important

-   Supplementary Table S1: Overview Existing Related Scales

-   Existing Scales: Review them in text

-   None of these do light exposure behaviour.

>>>>

Our circadian rhythm is in sync with the earth's 24-hour rotation cycle. In this synchronization, light plays the vital role. Light sends signals to the master oscillator of our brain, the suprachiasmatic nuclei (SCN), via the third class of photoreceptors- intrinsically photosensitive retinal ganglion cells (ipRGCs) [@berson2002phototransduction; @lucas2014measuring; @provencio1998retinal], thus entraining our biological clock [@duffy2005entrainment]. However, the temporal properties of light exposure, i.e., the time of day and the duration of light exposure, play a vital role in our health and well-being. These influences of light are known as non-image-forming (NIF) effects of light and include several physiological and psychological aspects such as secretion of melatonin, modulation of pupil size, skin temperature, alertness and other higher cognitive functions [@cajochen2000dose; @lok2018light; @siraji2021effects]. Wrong light exposure at an inappropriate time of day may lead to sleep disturbances [@chellappa2013acute; @santhi2012spectral]. Evening and nighttime bright light exposure may cause suppression of melatonin [@gooley2011exposure] and may cause a phase shift in the internal biological clock, thus, desynchronizing the body clock with nature's day-night circle. This reorganization of the body clock can create a series of adverse effects, including alteration of rhythmicity of several hormones, increased stress, cancer, and metabolic disruption, including obesity, type II diabetes, and heart diseases [@navara2007dark]

With the increased use of electric light, the natural temporal organization of the dark-light cycle has been compromised. People are exposed to light more than ever. Furthermore, nighttime electric light exposure is significantly increased day by day. In the US, more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara2007dark]. Our circadian clock signals the start of our melatonin secretion in our body based on the darkness of the night [@pauley2004lighting]. Since nights are no longer pure dark, most of the light-dependent systems of our body are disrupted. For example, studies suggest that electric monochromatic blue light exposure as low as 0.1 lux, which is almost equivalent to the brightness of full moonlight, may reduce the melatonin level [@brainard2002photoreception]. In turn, such changes in melatonin levels influence metabolism, immunity, fertility, and other hormonal balance, including adrenaline and thyroid hormone [@prendergast2002mammalian].

In recent years, the focus has been given in understanding the pathways underlying these influences of light. ipRGCs are mostly responsible for signalling the SCN when the ambient light changes [@gooley2003broad]. Additionally, ipRGCs also send signals to different brain regions, closely associated with our sleep, attention and emotion, thus influencing our work performance, sleep quality and mood (For a detailed discussion, see [@lok2018light; @siraji2021effects]). However, it is also essential to understand the behaviours people are engaging in, which ultimately quantify our light consumption. People are getting different types of light exposure due to their different daily life activities, including workplace habits, bedtime hygiene,  pastimes, and other social activities. Currently, little effort has been made to understand and capture these behaviours. Supplementary Table 1 summarizes relevant questionnaires to understand different light exposure related properties. Only a few questions of these questionnaires were related to light exposure related behaviour. For example, "Munich Chronotype Questionnaire" [@roenneberg2003life], a self-reporting chronotype identifier, has questions about time spent outdoors and the work environment. Popularly used "Pittsburgh Sleep Quality Index" [@buysse1989pittsburgh], a measure of sleep quality, also has questions about sleeping and wake-up time. However, none of these questionnaires provides a scaleable solution to capture light exposure related behaviour. To fill this gap, here we have reported the development process of a novel tool- "Light Exposure Behavior Assessment" (LEBA), to capture and quantify different light exposure related behaviour. LEBA will allow us to capture different light exposure related behaviour and gain insight into how different behaviour changes one's light exposure. Understanding these light exposure related behaviour will help us provide a personalized light diet to decrease the effects of inappropriate light exposure.
